---
output:
  html_document:
    keep_md: yes
    toc: no
    self_contained: no
  pdf_document:
    toc: yes
---

#### *Marcus W. Beck, marcusb@sccwrp.org, Raphael D. Mazor, raphaelm@sccwrp.org, Susanna Theroux, susannat@sccwrp.org, Kenneth C. Schiff, kens@sccwrp.org*

[![Travis-CI Build Status](https://travis-ci.org/SCCWRP/SQI.svg?branch=master)](https://travis-ci.org/SCCWRP/SQI)
 [![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/SCCWRP/SQI?branch=master&svg=true)](https://ci.appveyor.com/project/SCCWRP/SQI)
[![DOI](https://zenodo.org/badge/154087271.svg)](https://zenodo.org/badge/latestdoi/154087271)

# Overview 

This package provides functions to calculate a stream quality index using stream data.  The index requires biological, chemical, and physical data.

# Installing the package

The development version of this package can be installed from Github:

```{r eval = F, message = F}
install.packages('devtools')
library(devtools)
install_github('SCCWRP/SQI')
library(SQI)
```

# Usage

The core function is `sqi()`: 

```{r, message = F, warning = F, echo = F}
devtools::load_all()
```
```{r}
head(sampdat)
sqi(sampdat)
```

